---
title: "W_UP_01"
author: "Issa Darrouj"
date: "fall 2025"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(pushups~position,data=mydata)
```
  
The first quartile of the "Skill" players is bigger than the third quartile of the "Line" players. I believe that based on what Dr.K told us that in these situations there will be a statistical difference and that's what I think I will observe.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

  
I observed that there are in total 8 "LINE" players and 22 "SKILL" players. The average number of pushups that the "LINE" players can do is 17.12500, while the "SKILL" players on average can do 49.72727 pushups.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
t.test(pushups~position,data=mydata)
```
The chances of getting a result like this if there is no difference in means between group LINE and group SKILL is equal to .000009421. Such a really low p-value like that allowed me to conclude that there is a really big margin between the LINE players and the SKILL players.  

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In this write up, I learned how to plug in data whether it's a boxplot or favstats or t-test. I was able to observe all the numerical data. For example, in the boxplot chart I was able to analyze that the SKILL players where able to do more pushups because their first quartile is already bigger than the LINE players third quartile. Another example is that in the favstats I was able to get the exact number of players in both LINE and SKILL players and their average number of pushups, and for sure the SKILL players average number of pushups was way larger than the LINE players. Last but not least, in the t-test, I was able to get the p-value which was .000009421 and this value is so low that made me sure of my conclusion that there really is a big margin between LINE and SKILL players.  